### 2022-11-15 NSF2022/Description/summary.tex
last few changes

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}
\linespread{1.05}
\begin{document}
\section*{Summary}

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis, and
numerical simulations of collective dynamics and self-assembly arising
from attractive interactions between dipolar/nematic particles in a
suspension. Physicists model such a self-assembly using particles
possessing a biphasic material label on either half, with one more
hydrophobic than the other. Hydrophobic surfaces experience a
non-additive long-range attraction called the hydrophobic force. This
force is a major source of nonspecific interactions in biology and soft
matter. Despite its ubiquity, theoretical developments explaining its
basic underlying principles have come relatively late. Motivated by its
broad applicability, the PIs recently developed a novel and intuitive
mathematical model, called the hydrophobic attraction potential model,
based on the linear response of water to surface perturbations. This
model was used to show, for the first time, self-assembly of such
bipolar particles into vesicle-like structures using moving domain
elliptic partial differential equations (PDEs).

The PIs propose to analyze the elliptic PDEs, develop fast and accurate
numerical algorithms, and apply their hydrophobic attraction potential
model to more general self-organization dynamics. They aim to generalize
the linear-response model to a wider class of hydrophobic interactions,
and numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on
the kinetic theory to investigate the rheological properties of the
assembly of particles with tunable hydrophobicity. The unifying aspects
of the project will establish a platform for efficiently simulating the
collective dynamics of large numbers of particles, and focus on
rigorous, mathematical analysis of the underlying model equations in
complex geometries. The project supports undergraduate and graduate
student collaborators.

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules
with non-uniform hydrophobicity on their boundaries. The main ingredient
is a nonlocal interaction through the solution of moving domain elliptic
PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the
mathematical model in distinguished limits to make connections with
continuum models, designing efficient and high-order numerical
algorithms for large-scale two- and three-dimensional simulations with
confinement, and developing a kinetic theory to quantify both the polar
and nematic characteristics in the collective dynamics.

@@

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from Applied Mathematics.

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}
%\linespread{1.05}
\begin{document}
%\section*{Summary}

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis, and
numerical simulations of collective dynamics and self-assembly arising
from amphiphilic attractive interactions between finite-sized bipolar
particles in a suspension. Experimentalists study amphiphilic
self-assembly using particles with a biphasic
material label.
These amphiphilic particles experience a non-additive, long-range
attraction that is a ubiquitous source of nonspecific interactions in
biology and soft matter. Motivated by its broad applicability, the PIs
recently developed a mathematical model for phase-field-mediated
interactions between particles. This model was used to show, for the
first time, self-assembly of bipolar particles into vesicle-like
structures using moving domain elliptic partial differential equations
(PDEs).

The PIs propose to analyze the elliptic PDEs, develop fast and accurate
numerical algorithms, and apply their hydrophobic attraction potential
model to more general self-organization dynamics. They aim to generalize
the linear model to a wider class of hydrophobic interactions, and
numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on
kinetic theory to investigate the rheological properties of the assembly
of particles with tunable hydrophobicity. The unifying aspects of the
project will establish a platform for efficiently simulating the
collective dynamics of large numbers of particles, and focus on
rigorous, mathematical analysis of the underlying model equations in
complex geometries. The project supports undergraduate and graduate
student collaborators.

\vspace{-0.1in}
\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules
with non-uniform hydrophobicity on their boundaries. The main ingredient
is a nonlocal interaction through the solution of moving domain elliptic
PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the
mathematical model in distinguished limits to make connections with
continuum models, designing efficient and high-order numerical
algorithms for large-scale two- and three-dimensional simulations with
confinement, and developing a kinetic theory to quantify both the polar
and nematic characteristics in the collective dynamics.

@@

\vspace{-0.1in}
\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates variational techniques and offers
insight into fundamentals of self-organization and collective dynamics.
The project brings socially consequential research into the classroom
and offers undergraduates the opportunity to train alongside faculty and
graduate students. With its unique combination of mathematical modeling,
analysis, and scientific computing, the project highlights the potential
advancement of STEM from Applied Mathematics.
